Synthesising Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-08 papers/termination/paper.tex
Equivalently -> alternatively

We note that some termination arguments require lexicographic ranking functions, or
equivalently, ranking functions whose co-domain is a countable ordinal, rather than just $\mathbb{N}$.

>>>>

We note that some termination arguments require lexicographic ranking functions, or
alternatively, ranking functions whose co-domain is a countable ordinal, rather than just $\mathbb{N}$.
